### 2012-06-26 trunk/ijcis-pos-model/sources/timeRepresentation.tex
final changes

%\begin{definition}
\textbf{Ill-known time interval}\\
An ill-known time interval denoted by $\left[X, Y\right]$ is a precise time interval whose boundaries are not precisely known. The ill-known time interval is defined by two ill-known  time points, namely $X$,$Y$. The evaluation of the ill-known time interval is given iby equations \eqref{ill-known-pos},\eqref{ill-known-nec}.

@@

\vspace*{13pt}
\begin{center}
{
\includegraphics[scale=1]{./graphs/open-time-interval.pdf}
\label{fig:example-open-time-interval}
}
\end{center}
%\centerline{ \psfig{file=./graphs/Y-time-point.eps}}
\vspace*{10pt}
\fcaption{Possibility distribution for $Y$, and possibility and necessity measures for the open ill-known point, $X$}
\vspace*{13pt}

>>>>

An ill-known time interval denoted by $\left[X, Y\right]$ is a precise time interval whose boundaries are not precisely known. %The ill-known time interval is defined by two ill-known  time points, namely $X$,$Y$. The evaluation of the ill-known time interval is given by equations \eqref{ill-known-pos},\eqref{ill-known-nec}.

\begin{definition}
\emph{Ill-known time interval}
Let $\T$ be the time domain, and $X$, $Y$ two ill-known values in the time domain. An ill-known time interval is given by $\left[X, Y\right]$. The evaluation of the ill-known time interval is given by equations \eqref{ill-known-pos},\eqref{ill-known-nec}. We will note $\I_{PVP}$ the set of all the ill-known time intervals.

\end{definition}

@@

\begin{samepage}
\vspace*{13pt}
\begin{center}
{
\includegraphics[scale=1]{./graphs/open-time-interval.pdf}

}
\end{center}
%\centerline{ \psfig{file=./graphs/Y-time-point.eps}}
\vspace*{10pt}
\fcaption{\label{fig:example-open-time-interval}Possibility distribution for $Y$, and possibility and necessity measures for the open ill-known point, $X$}
\vspace*{13pt}
\end{samepage}
